Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
moved sec 2.4 into sec 3
wordings

\item We provide experimental results showing that
our fully automatic program synthesis based approach is able to synthesise 
stable controllers
%sound parametric solutions for digital stabilizing controllers
for a set of intricate benchmarks taken from 
the literature in a reasonable amount of time 
(the median runtime for our benchmark set is 197s, 
implying that half of the controllers can be synthesised in less
than 5 minutes).

@@

%\red{[TO BE COMPLETED.]}

% We use CounterExample-Guided Inductive Synthesis (CEGIS), as
% illustrated in Fig~\ref{fig:CEGIS}.

>>>>

\item We provide experimental results showing that our fully automatic
program synthesis based approach is able to synthesise stable controllers
for a set of intricate benchmarks taken from the literature efficiently: the
median runtime for our benchmark set is $197$s, i.e., half of the
controllers can be synthesised in less than five minutes.

@@

%\red{[TO BE COMPLETED.]}
% We use CounterExample-Guided Inductive Synthesis (CEGIS), as
% illustrated in Fig~\ref{fig:CEGIS}.
